Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex
clarified Russian data

\section{Data Sets}
The data used for this work came from English Penn Tree Bank CoNLL dependency training data \noteJH{cite?} 
%\noteJE{wait a minute, the bnews is not from CoNLL!  It is merely in CoNLL format.  It is from Ariya Rastrow, and is automatically parsed, I think.  We should be comparing on hand-parsed data.}  
and the Russian National Corpus\footnote{\url{http://ruscorpora.ru/en/}} \cite{russiancorpus} \noteJE{give citation}.

We generated link parses using the AbiWord/CMU link grammar parser version 5.0.8 \cite{LINKPARSER-2014}.  The parser's coverage is not perfect: we obtained complete, connected parses for only \input{figure/conll_analysis_sentences_total.tex}of (\input{figure/conll_analysis_sentences_original.tex}) English sentences and only 206 (of 10,000) Russian sentences, discarding the other sentences. 
%\noteJE{fill these !!! in automatically} 
These two languages have the most complete lexicons at present, although lexicons for seven other languages are available.

>>>>

\section{Data Sets}
We used the English sentences from the CoNLL 2007 Shared Task \cite{CONLL-SHARED-2007}, a subset of the Penn Treebank for which {\em single}-headed reference parses are available.  We also used a prefix of the Russian National Corpus.\footnote{That is, a prefix when considering the files in Unix sort order by filename.  We dropped sentences with $\leq 2$ words, as well as file 22592319, which appeared to contain charts.}

We generated link parses using the AbiWord/CMU link grammar parser version 5.0.8 \cite{LINKPARSER-2014}.  The parser's coverage is not perfect: we obtained connected parses for only \input{figure/conll_analysis_sentences_total.tex}(of \input{figure/conll_analysis_sentences_original.tex}$\!\!$) English sentences and only 8,018 (of 10,000) Russian sentences, discarding the other sentences.\footnote{For Russian only, we permitted the parser to drop words if necessary.  Otherwise only 208 sentences were parseable.}
These two languages have the most complete lexicons at present, although lexicons for 7 other languages are available.
